ST563 Final Project

### 2021-04-19 DRAFT.Rmd
Add draft .Rmd file and output pdf Took pertinent sections from the ST563-FP.Rmd file and made some small changes to adapt code.

---
title: "ST563 Final Project"
author: "Mana Azizsoltani"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: 
  pdf_document:
    toc: true
    toc_depth: 1
fontsize: 12pt
---

@@

```{r methods}
# Make table of methods
cl <- c("Classification Tree", "Random Forest", "Support Vector Machine (SVM)",
        "KNN Classification", "Logistic Regression")
reg <- c("Boosted Tree", "Random Forest", "Multiple Linear Regression (MLR)", 
          "KNN Regression", "LASSO Regression")
kable(data.frame("Classification" = cl, "Regression" = reg), caption = "ML Methods") %>% 
  row_spec(0, bold=TRUE) %>% collapse_rows(columns = 1, latex_hline = "none") %>% 
  kable_styling(latex_options = "hold_position")
```

@@

  * `caret`: to do the heavy lifting of training and tuning the models
  * `tidyverse`: for all the data reading and wrangling
  * `knitr`: for rmarkdown table outputs
  * `rmarkdown`: for output documents
  * `corrplot`: for correlation structure visualization
  * `leaps`: for subset selection
  * `rpart`: fitting the basic classification tree
  * `rpart.plot`: visualization of the classification tree
  * `randomForest`: fitting random forest models
  * `kernlab`: fitting the support vector machine
  * `class`: fitting the k-nearest neighbor model
  * `glmnet`: fitting the LASSO model
  * `gbm`: fitting the boosted tree model

@@

The tree-based, LASSO, and K-nearest neighbors models require parameters to be tuned (more on those later). Since we used the `caret` package in R to fit all of our models, we used the tunes of the parameters that were deemed "best" by the `train()` function.

@@

## Basic Tree  
The basic classification or regression tree is based on partitioning the data into subgroups using simple binary splitting. Initially, all objects are considered a single group. Then, the group is repeatedly binarily split into two subgroups based on the criteria of a certain variable. In the classification setting, we classify the observations in a specific region with majority vote, while in the context of regression the mean of the group is used for prediction. We want to grow the tree as big as we can, and then prune it back using cost-complexity pruning. This is done to not overfit the data, but pruning increases the bias. The pruning parameter needs to be tuned, which is done automatically in the `caret` package.

The advantage of using a basic tree is that it is easy to understand and has a good interpretability, which is not something that translates over to ensemble methods like the random forest. Additionally, the basic classification or regression tree is not very computationally expensive, unlike the random forest, boosting, and the support vector machine. We used the `caret` and `rpart` packages in R to fit our trees.

@@

## Support Vector Machine  
A support vector machine (SVM) is a classification method, which maximizes the margin between groups by choosing the "line" with the widest "margin", while still allowing for error. Line in quotation marks because with higher-dimensional data, the "line" is a hyperplane. Similarly, the "margin" does not exist in the sense of a clean margin between two, since the model is allowing for some error. The support vectors are the points closest to the middle, these carry the most weight in classification.  This is because they are most prone to error and are deciding factors of where the classification line could go. The SVM was built using cross validation, where multiple SVMs were built using different values for the cost parameter. The `tune()` function builds these models and the best is selected,  in this case the cost parameter of 0.01 was the best. For this data, the SVM correctly predicted all observations. If the data were much larger, one would expect the model to be less effective due to the extra noise.

```{r svm}
#### CLASSIFICATION ####
# Fit support vector machine for H1
svm.class <- tune(svm, class~ . ,data=trn ,kernel ="linear", ranges=list(cost=c(0.001, 0.01, 0.1, 1,5,10,100) ))
best.mod <- svm.class$best.model
# Obtain confusion matrix and results for H1
svm.class.pred <- predict(best.mod, newdata = tst)
table(svm.class.pred, tst$class)

# Print out results in a list
#list("Results" = svm.class.res,
#     "Confusion Matrix" = svm.class.CM$table)
```

## K-Nearest Neighbors (KNN)  
K-NN is a "model free" approach, meaning that it doesn't assume any probability model on the data. Given an observation, $\boldsymbol{x}$, we want to find the k training observations that are "closest" to $\boldsymbol{x}$, and then either classify the new observation using majority vote among these k neighbors or predict the new observation by averaging the closest k neighbors. We define "closeness" based on Euclidean distance in our model. As this is the case, we need to center and scale the data, so that different scales of measurement are kept constant.

The K-nearest neighbors model is relatively intuitive and simple and has no underlying assumptions, making it a good model to consider. In our classification, we are only using it for a binary classification, but it is also very easy to extend the K-NN model to multiple classes. On the other hand, the K-NN algorithm is very sensitive to outliers, high dimensional data, and imbalanced data.

The number (k) of closest neighbors is a parameter that needs tuning. We used the `class` and `caret` packages in R to fit this model. Based on our cross-validation, we used a k value of 5.

```{r knn}
#### REGRESSION ####
# Fit knn regression model
knn.reg <- train(form.reg, data = trn, method = "knn",
                 trControl = trctrl, preProcess = c("center", "scale"))

# Obtain RMSE and results
knn.reg.pred <- predict(knn.reg, newdata = tst)
knn.reg.rmse <- sqrt(mean((knn.reg.pred - tst$quality)^2))

#### CLASSIFICATION ####
# Fit knn classification model
trn.class <- wine$class[ind]
trn.knn <- trn[,-13]
tst.knn <- tst[,-13]
knn.class <- knn(trn.knn, tst.knn, trn.class, k=5)

# Obtain confusion matrix and misclassification rate
table(knn.class, tst$class)
(37+39)/(37+39+140+104)

# Print out results in a list
#list("RMSE" = knn.reg.rmse,
#     "Class Results" = knn.class.res)
```

## Logistic Regression  
The logistic regression model uses the "logit" function, $log(\frac{p}{1-p})$, which links the mean to the linear form of the regression model, $\boldsymbol{X\beta}$. Using it for binary classification, we round the fitted values either up or down to 1 or 0. The logistic regression function is defined as  
$$
\ln \left( \frac{p(x)}{1-p(x)} \right) = x'\beta, \qquad \text{where }p(x) = (1+e^{-x'\beta})
$$

The logistic regression model assumes that each observation is independent, that there is little or no multicollinearity among the predictors, and that there is a linear relationship between the predictor variables and log odds. This differs from the typical regression model, where the residuals must be normally distributed and have constant variance.

To fit the logistic regression model, we used the `glm()` function in base R. The advantages to using a logistic regression model are similar to those for the basic classification tree: it is not computationally expensive and easy to interpret the results. On the other hand, one of the major drawbacks to using a logistic regression model is that it is subject to the distributional assumptions on the data and errors mentioned above. If our assumptions are broken, our predictions may not be very reliable.

```{r logit}
#### CLASSIFICATION ####
# Fit logistic regression model
glm.class <- glm(form.class, data = trn, family = binomial(link = "logit"))

# Obtain confusion matrix and results for H2
glm.class.pred <- predict(glm.class, newdata = tst, type = "response")
glm.class.pred <- glm.class.pred %>% round() %>% as.factor()
glm.class.CM <- confusionMatrix(glm.class.pred, ifelse(tst$class == "low", 1, 0) %>% as.factor())
glm.class.res <- c(glm.class.CM$overall[1], glm.class.CM$byClass[1:2])

# Print out results in a list
#list("Results" = glm.class.res,
#     "Confusion Matrix" = glm.class.CM$table)
```

## LASSO Regression
LASSO, which stands for Least Absolute Shrinkage and Selection Operator works to shrink beta coefficient estimators towards zero using a penalty term. This is different from traditional shrinkage methods since the form of the LASSO penalty actually forces some of the coefficients to exactly zero. This helps achieve variable selection and yields sparser models, similar to subset selection. In particular, the LASSO estimate minimizes:
$$
\sum_{i=1}^n\left( y_i - \beta_0 - \sum_{j=1}^p\beta_jx_{ij}\right)^2 + \lambda \sum_{j=1}^p|\beta_j| = RSS + \lambda \sum_{j=1}^p|\beta_j|
$$
where $\lambda$ is the penalty parameter, with p different predictors.

The main benefits of using LASSO are the variable selection property, the computational efficiency, and the interpretability. Plus, as with any regularization method, it can help to avoid overfitting with a very flexible model. On the other hand, some of the pitfalls of LASSO are that the selected variables could be highly biased, correlation among predictors is not very well dealt with, and the feature selection may not be stable over different bootstrapped samples.

To fit the LASSO regression model, we used the `glmnet` package in R.

```{r lasso}
#### REGRESSION ####
# Fit LASSO to the data
lasso.reg <- train(form.reg, data = trn, method = "glmnet", trControl = trctrl, 
                   tuneGrid = expand.grid(.alpha=1, .lambda=0.00175))

lasso.reg.pred <- predict(lasso.reg, newdata = tst)
lasso.reg.rmse <- sqrt(mean((lasso.reg.pred - tst$quality)^2))
#lasso.reg.rmse
```

## Boosted Tree
Boosting is the process of slowly training trees to avoid overfitting. The general approach is as follows: the trees are grown sequentially, where each subsequent tree is grown on a modified version of the original data, while the predictions are continuously updated as the trees are grown. The model has three parameters that need tuning:

  * $B$: the number of trees
  * $\lambda$: the shrinkage parameter, which is a small positive number that controls the rate at which the boosting learns
  * $d$: the number of splits in each tree, which controls the complexity of the boosted ensemble

The main benefit of using boosting is to reduce overfitting. It often yields the best results in terms of the ensemble learning methods. Like the random forest model, since boosting is an ensemble learning technique, it will have a lower variance than other methods. Also, there is no need to scale down variables or create any dummy variables for categorical variables. All that said, boosting is not without its shortcomings; it does not do well with high dimensionality, it's not very interpretable (since it is a sort of blackbox algorithm), and it is relatively expensive computationally.

```{r boost}
#### REGRESSION ####
# Fit the regression boosted tree model 
boost.reg <- train(form.reg, data = trn, method = "gbm",
                trControl = trctrl, verbose = FALSE)

# Obtain RMSE and results
boost.reg.pred <- predict(boost.reg, newdata = tst)
boost.reg.rmse <- sqrt(mean((boost.reg.pred - tst$quality)^2))
#boost.reg.rmse
```

The biggest benefit to using a multiple linear regression model is its interpretability and ease of use. The coefficients can be computed efficiently and they are have clear and easy interpretations. It is also possible to make inference on any of the variables or linear combination of variables. The most signficiant drawback of using the multiple linear regression model is that, like the logistic regression model, it is subject to distributional assumptions, meaning that if the assumptions are violated, our estimates and inference will be unstable at best and invalid at worst.

@@

```{r create.df}
# Create data frame output for regression models
df.reg <- rbind.data.frame(boost.reg.rmse, rf.reg.rmse,
                           lm.reg.rmse, knn.reg.rmse, 
                           lasso.reg.rmse) %>% round(4)
df.reg$method <- reg
colnames(df.reg) <- c(LETTERS[1:2])
df.reg <- df.reg %>% select("B", "A")
colnames(df.reg) <- c("Regression Method", "Root MSE")

# Create data frame output for classification models
df.class <- rbind.data.frame(tree.class.res, rf.class.res, 
                             svm.class.res, knn.class.res, 
                             glm.class.res) %>% round(4)
df.class$method <- cl
colnames(df.class) <- c("A", "B", "C", "D")
df.class <- df.class %>% select("D", "A", "B", "C")
colnames(df.class) <- c("Classification Method", "Accuracy", "Sensitivity", "Specificity")
```

@@

Based on the output, the best model for both classification and regression was the random forest. This was not a surprise, since the ensemble methods tend to outperform regular methods. This is further exemplified by the lower-than-average root MSE of the boosted tree model. The other models all did about the same in terms of prediction accuracy. For classification, all of the non-aforementioned methods were in the low 70s in terms of prediction accuracy, while the non-ensemble regression models had root MSEs right around 0.65.

The fact that the random forest and boosted tree models so drastically outperformed the basic classification tree did not come as a surprise, since as an average of many classification trees, ensemble methods generally improve prediction accuracy and reduce overall variance. We suspect that other ensemble methods, such as bagging, may also be able to get higher prediction accuracies. One of the main disadvantages to using ensemble techniques like the random forest is the fact that they tend to be very computationally intensive. The basic classification tree, logistic regression, and KNN models took significantly less time to run than the random forest and the SVM, but they were less accurate in their predictions. If we wanted to run an ensemble method on a very large data set with a lot of features, it would be a computational nightmare.

# Conclusion  
With the recent push for quantitative solutions in industries like agriculture, there has been an emphasis on using machine learning to solve a variety of problems requiring prediction and inference. In particular, the viticulture industry stands to gain a lot from such methods, since historically it has not interacted much with the world of analytics. In this study, we went through a number of different machine learning techniques, assessing prediction accuracy in both classification and regression contexts.

@@

## Limitations  
The multiple linear regression and logistic regression models were both subject to certain distributional and model assumptions, which were not explicitly tested or checked. Since the objective of this project was to predict rather than make inference, we did explicitly check the model assumptions.

@@

```{r appendix, eval=FALSE, echo=FALSE}
#### SETUP STUFF ####
# Set default chunk options
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)

# Load necessary libraries
library(tidyverse) # so many things
library(knitr) # making nice tables
library(caret) # training models & CV
library(leaps) # subset selection
library(corrplot) # visualize correlation
library(rmarkdown) # for output documents
library(rpart) # fitting classification tree
library(rpart.plot) # visualization of classification tree
library(randomForest) # fitting random forest model
library(kernlab) # fitting SVM
library(class) # fitting kNN model
library(glmnet) # fitting LASSO 
library(gbm) # fitting the boosted tree model
library(kableExtra) # making bolded headers for tables

# Set seed for reproducibility
set.seed(702)

#### METHODS TABLE ####
# Make table of methods
cl <- c("Classification Tree", "Random Forest", "Support Vector Machine (SVM)",
        "KNN Classification", "Logistic Regression")
reg <- c("Boosted Tree", "Random Forest", "Multiple Linear Regression (MLR)", 
          "KNN Regression", "LASSO Regression")
kable(data.frame("Classification" = cl, "Regression" = reg), caption = "ML Methods") %>% 
  row_spec(0, bold=TRUE) %>% collapse_rows(columns = 1, latex_hline = "none") %>% 
  kable_styling(latex_options = "hold_position")

#### DATA PARTITIONING ####
# Prepare data for classification
wine$class <- ifelse(wine$quality <= 5, "low", "high") %>% as.factor()

# Create Data Partition
ind <- createDataPartition(wine$quality, p = .75, list = FALSE)

# Create train/test data for H1
trn <- wine[ind,]
tst <- wine[-ind,]

#### CROSS VALIDATIONN ####
# Specify the cross-validation method (5-fold CV)
trctrl <- trainControl(method = "cv", number = 5)

#### VARIABLE SELECTION ####
# Write preliminary model  
model.class.pre <- class ~ .

# Plot variable importance
vimp.class <- ggplot(VIrf.pre.class.sort, aes(x = X, y = MeanDecreaseAccuracy)) +
                geom_bar(stat = 'identity', position = 'dodge', fill="lightblue") +
                theme(axis.text.x = element_text(angle = 30, hjust = 1)) +
                ylab("Mean Decrease in Accuracy") + xlab("Predictor") +
                ggtitle("Variable Importance") + 
                geom_hline(yintercept = .005, lty = 2, colour = "darkblue")
vimp.class

# Create model and get summary output
lm.sub <- regsubsets(quality ~ ., data = wine[,-13], nvmax = 11)
smre <- lm.sub %>% summary()

# Best subset selection
best.betas <- coef(lm.sub, id = 6) %>% round(2)

#### WRITE FORMULAS ####
# Write formula for regression models
form.reg <- quality ~ volatile.acidity + chlorides + pH + 
            total.sulfur.dioxide + sulphates + alcohol

# Write formula for classification models
form.class <- class ~ alcohol + sulphates + density +
              volatile.acidity + total.sulfur.dioxide

#### BASIC CLASSIFICATION TREE ####
# Fit classification tree model
tree.class <- train(form.class, data = trn, method = "rpart",
                    trControl = trctrl)

# Print out classification tree visualization
tree.class.out <- rpart(form.class, data = trn, cp = 0.01971326)
rpart.plot(tree.class.out, main="Classification Tree")

#### RANDOM FOREST ####
# Fit the regression random forest model 
rf.reg <- train(form.reg, data = trn, method = "rf",
                trControl = trctrl, importance = TRUE)

# Fit the classification random forest model
rf.class <- train(form.class, data = trn, method = "rf",
                trControl = trctrl, importance = TRUE)

#### SUPPORT VECTOR MACHINE ####
# Fit support vector machine for H1
svm.class <- train(form.class, data = trn, method = "svmRadial", 
                   preProcess = c("center", "scale"),
                   trControl = trctrl, tuneLength = 10)

# Obtain confusion matrix and results for H1
svm.class.pred <- predict(svm.class, newdata = tst)
svm.class.CM <- confusionMatrix(svm.class.pred, tst$class)
svm.class.res <- c(svm.class.CM$overall[1], svm.class.CM$byClass[1:2])

#### KNN ####
# Fit knn regression model
knn.reg <- train(form.reg, data = trn, method = "knn",
                 trControl = trctrl, preProcess = c("center", "scale"))

# Obtain RMSE and results
knn.reg.pred <- predict(knn.reg, newdata = tst)
knn.reg.rmse <- sqrt(mean((knn.reg.pred - tst$quality)^2))

# Fit knn classification model
knn.class <- train(form.class, data = trn, method = "knn",
                   trControl=trctrl, preProcess = c("center", "scale"))

# Obtain confusion matrix and results
knn.class.pred <- predict(knn.class, newdata = tst)
knn.class.CM <- confusionMatrix(knn.class.pred, tst$class)
knn.class.res <- c(knn.class.CM$overall[1], knn.class.CM$byClass[1:2])

#### LOGISTIC REGRESSION ####
# Fit logistic regression model
glm.class <- glm(form.class, data = trn, family = binomial(link = "logit"))

# Obtain confusion matrix and results for H2
glm.class.pred <- predict(glm.class, newdata = tst, type = "response")
glm.class.pred <- glm.class.pred %>% round() %>% as.factor()
glm.class.CM <- confusionMatrix(glm.class.pred, ifelse(tst$class == "low", 1, 0) %>% as.factor())
glm.class.res <- c(glm.class.CM$overall[1], glm.class.CM$byClass[1:2])

#### LASSO ####
# Fit LASSO to the data
lasso.reg <- train(form.reg, data = trn, method = "glmnet", trControl = trctrl, 
                   tuneGrid = expand.grid(.alpha=1, .lambda=0.00175))

lasso.reg.pred <- predict(lasso.reg, newdata = tst)
lasso.reg.rmse <- sqrt(mean((lasso.reg.pred - tst$quality)^2))

#### BOOSTING ####
# Fit the regression boosted tree model 
boost.reg <- train(form.reg, data = trn, method = "gbm",
                trControl = trctrl, verbose = FALSE)

# Obtain RMSE and results
boost.reg.pred <- predict(boost.reg, newdata = tst)
boost.reg.rmse <- sqrt(mean((boost.reg.pred - tst$quality)^2))

#### MLR ####
lm.reg <- train(form.reg, data = trn, method = "lm",
                trControl = trctrl)

# Obtain RMSE and results for linear model
lm.reg.pred <- predict(lm.reg, newdata = tst)
lm.reg.rmse <- sqrt(mean((lm.reg.pred - tst$quality)^2))

#### OUTPUT RESULTS ####
# Create data frame output for regression models
df.reg <- rbind.data.frame(boost.reg.rmse, rf.reg.rmse,
                           lm.reg.rmse, knn.reg.rmse, 
                           lasso.reg.rmse) %>% round(4)
df.reg$method <- reg
colnames(df.reg) <- c(LETTERS[1:2])
df.reg <- df.reg %>% select("B", "A")
colnames(df.reg) <- c("Regression Method", "Root MSE")

# Create data frame output for classification models
df.class <- rbind.data.frame(tree.class.res, rf.class.res, 
                             svm.class.res, knn.class.res, 
                             glm.class.res) %>% round(4)
df.class$method <- cl
colnames(df.class) <- c("A", "B", "C", "D")
df.class <- df.class %>% select("D", "A", "B", "C")
colnames(df.class) <- c("Classification Method", "Accuracy", "Sensitivity", "Specificity")

# Smash tables next to each other using kable
kable(df.reg, caption = "Regression Model Results", format = "latex") %>% 
  row_spec(0, bold=TRUE) %>% collapse_rows(columns = 1, latex_hline = "none") %>%
  kable_styling(latex_options = "HOLD_position")
kable(df.class, caption = "Classification Model Results", format = "latex") %>% 
  row_spec(0, bold=TRUE) %>% collapse_rows(columns = 1, latex_hline = "none") %>%
  kable_styling(latex_options = "HOLD_position")
```

>>>>

---
title: "ST563 Final Project"
author: "Final Project Group 6"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: 
  pdf_document:
    toc: true
    toc_depth: 1
fontsize: 12pt
---

@@

```{r methods}
# Make table of methods
cl <- c("Classification Tree", "Random Forest")
reg <- c("Multiple Linear Regression (MLR)", "Random Forest")
kable(data.frame("Classification" = cl, "Regression" = reg), caption = "ML Methods") %>% 
  row_spec(0, bold=TRUE) %>% collapse_rows(columns = 1, latex_hline = "none") %>% 
  kable_styling(latex_options = "hold_position")
```

@@

  * `caret`: to do the heavy lifting of training and tuning the models
  * `tidyverse`: for all the data reading and wrangling
  * `knitr`: for rmarkdown table outputs
  * `rmarkdown`: for output documents
  * `corrplot`: for correlation structure visualization
  * `leaps`: for subset selection
  * `rpart`: fitting the basic classification tree
  * `rpart.plot`: visualization of the classification tree
  * `randomForest`: fitting random forest models

@@

@@

The biggest benefit to using a multiple linear regression model is its interpretability and ease of use. The coefficients can be computed efficiently and they are have clear and easy interpretations. It is also possible to make inference on any of the variables or linear combination of variables. The most signficiant drawback of using the multiple linear regression model is that it is subject to distributional assumptions, meaning that if the assumptions are violated, our estimates and inference will be unstable at best and invalid at worst.

## Classification Tree  
The basic classification tree is based on partitioning the data into subgroups using simple binary splitting. Initially, all objects are considered a single group. Then, the group is repeatedly binarily split into two subgroups based on the criteria of a certain variable. In the classification setting, we classify the observations in a specific region with majority vote. We want to grow the tree as big as we can, and then prune it back using cost-complexity pruning. This is done to not overfit the data, but pruning increases the bias. The pruning parameter needs to be tuned, which is done automatically in the `caret` package.

The advantage of using a basic tree is that it is easy to understand and has a good interpretability, which is not something that translates over to ensemble methods. Additionally, the basic classification tree is not very computationally expensive, unlike the random forest, boosting, and support vector machine. We used the `caret` and `rpart` packages in R to fit our trees.

@@

@@

```{r create.df}
# Create data frame output for regression models
df.reg <- rbind.data.frame(lm.reg.rmse, rf.reg.rmse) %>% round(4)
df.reg$method <- reg
colnames(df.reg) <- c(LETTERS[1:2])
df.reg <- df.reg %>% select("B", "A")
colnames(df.reg) <- c("Regression Method", "Root MSE")

# Create data frame output for classification models
df.class <- rbind.data.frame(tree.class.res, rf.class.res) %>% round(4)
df.class$method <- cl
colnames(df.class) <- c("A", "B", "C", "D")
df.class <- df.class %>% select("D", "A", "B", "C")
colnames(df.class) <- c("Classification Method", "Accuracy", "Sensitivity", "Specificity")
```

@@

Based on the output, the best model for both classification and regression was the random forest. This was not a surprise, since the ensemble methods tend to outperform regular methods. As an average of many classification trees, ensemble methods generally improve prediction accuracy and reduce overall variance. We suspect that other ensemble methods, such as bagging or boosting, may also be able to yield higher prediction accuracies.

One of the main disadvantages to using ensemble techniques like the random forest is the fact that they tend to be very computationally intensive. The basic classification tree and multiple linear regression model took significantly less time to run than the random forest and the SVM, but they were less accurate in their predictions. If we wanted to run an ensemble method on a very large data set with a lot of features, it would be a computational nightmare.

# Conclusion  
With the recent push for quantitative solutions in industries like agriculture, there has been an emphasis on using machine learning to solve a variety of problems requiring prediction and inference. In particular, the viticulture industry stands to gain a lot from such methods, since historically it has not interacted much with the world of analytics. In this study, we went through various machine learning techniques, assessing prediction accuracy in both classification and regression contexts.

@@

## Limitations  
The multiple linear regression model is subject to certain distributional and model assumptions, which were not explicitly tested or checked. Since the objective of this project was to predict rather than make inference, we didn't explicitly check the model assumptions.

@@
